---
title: "R Markdown and Leaflet"
author: "Hebert Ladera Castillo"
date: "June 15 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
We create a web page using R Markdown that features a map created with Leaflet 
and host our webpage on either GitHub Pages.

Our webpage must contain the date that we created the document, and it must contain a map created with Leaflet.

### The code of the map

```{r}
library(leaflet)
my_map <- leaflet() %>% addTiles() %>%
        addMarkers(lat=20.31704, lng=-87.35409, 
             popup="My favorite Park")
my_map
```



knitr::opts_chunk$set(echo = TRUE)

rm(list = ls()) # clear all environment variables

suppressPackageStartupMessages(library(leaflet))

suppressPackageStartupMessages(library(rgdal))

resource <- "https://raw.githubusercontent.com/datasets/geo-boundaries-world-110m/master/countries.geojson"

download.file(url = resource, destfile = "countries.geojson")

countries <- readOGR("countries.geojson", "OGRGeoJSON")

map <- leaflet(countries) %>% addTiles(group = "Layers:")

gdpColors <- colorQuantile("Greens", countries$gdp_md_est, n = 5)

popColors <- colorQuantile("Blues", countries$pop_est, n = 5)

map %>% addPolygons(
            
stroke = FALSE,
          
smoothFactor = 0.2,
            
fillOpacity = 1,
            
color =  ~ gdpColors(gdp_md_est),
            
group = "GDP"
  
  ) %>% addPolygons(
  
  stroke = FALSE,
  
  smoothFactor = 0.2,
  
  fillOpacity = 1,
  
  color = ~ popColors(pop_est),
  
  group = "Population"
  
  ) %>% addLegend(
  
  "bottomright",
  
  pal = gdpColors,
  
  values = ~ gdp_md_est,
  
  title = "GDP",
          
opacity = 1

) %>% addLegend(

"bottomright",

pal = popColors,

values = ~ pop_est,

title = "Population",

opacity = 1

) %>% addLayersControl(

baseGroups = c("Layers:"),

overlayGroups = c("GDP", "Population"),

options = layersControlOptions(collapsed = FALSE)

)
